---
title: "DATA 605: Homework 1"
author: "Philip Tanofsky"
date: "1/30/2021"
output: html_document
---

## Prompt

For this assignment, build the first letters for both your first and last name using point plots in R.

Then, write R code that will left multiply (%>%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the Identity matrix.  

Use a loop that changes the transformation matrix incrementally to demonstrate 1) shear, 2) scaling, 3)  rotation, and 4) projection in animated fashion.  

```{r eval=F}
# PT
x=c(rep(-1,500), seq(-1,0,length.out=1000), seq(-1,0,length.out=1000),
    rep(0,250), seq(0.25,.75,length.out=500), rep(.75,1000), seq(.75,1.25,length.out=500))

y=c(seq(-1,1,length.out=500), rep(0,1000), rep(1,1000), seq(0,1,length.out=250), 
    rep(1,500), seq(-1,1,length.out=1000), rep(1,500))

# T
#x=c(seq(0,.5,length.out=500), rep(.5,1000), seq(.5,1,length.out=500))
#y=c(rep(1,500), seq(-1,1,length.out=1000), rep(1,500))

# H (from prompt)
#x=c(rep(0,500), seq(0,1,length.out=1000), rep(1,500))
#y=c(seq(-1,1,length.out=500), rep(0,1000), seq(-1,1,length.out=500))

z=rbind(x,y)

# Confirm the 'PT' is showing based on prompt code
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

# Create Identify Matrix
trans_matrix <- diag(2)

# Multiply Identity matrix by the vector of points
# Realistically, the base identity matrix does not modify the vector of points
result <- trans_matrix %*% z

x11(title="Animation")

#result
# Display resulting plot, should be same as the initial plot
plot(result[2,]~result[1,], xlim=c(-10,10), ylim=c(-10,10))

# Add sleep so the animation will be easier to watch
Sys.sleep(1)

# Create matrix for shear
trans_matrix <- matrix(
  c(1, 0, 1.2, 1), nrow=2, ncol=2) 

result <- trans_matrix %*% z

# Display resulting plot, should be shear plot
plot(result[2,]~result[1,], xlim=c(-10,10), ylim=c(-10,10))

Sys.sleep(1)

# Create matrix for scale
trans_matrix <- matrix(
  c(2, 0, 0, 2), nrow=2, ncol=2) 

result <- trans_matrix %*% result

# Display resulting plot, should be scale plot
plot(result[2,]~result[1,], xlim=c(-10,10), ylim=c(-10,10))

Sys.sleep(1)

# Create matrix for rotation (90 degrees counterclockwise)
trans_matrix <- matrix(
  c(0, 1, -1, 0), nrow=2, ncol=2) 

result <- trans_matrix %*% result

# Display resulting plot, should be rotate plot
plot(result[2,]~result[1,], xlim=c(-10,10), ylim=c(-10,10))

Sys.sleep(1)

# Create matrix for projection (projection on the y axis)
trans_matrix <- matrix(
  c(0, 1, 0, 1), nrow=2, ncol=2) 

result <- trans_matrix %*% result

# Display resulting plot, should be projection plot
plot(result[2,]~result[1,], xlim=c(-10,10), ylim=c(-10,10))

```

## Looping

``` {r}
# PT
x=c(rep(-1,500), seq(-1,0,length.out=1000), seq(-1,0,length.out=1000),
    rep(0,250), seq(0.25,.75,length.out=500), rep(.75,1000), seq(.75,1.25,length.out=500))

y=c(seq(-1,1,length.out=500), rep(0,1000), rep(1,1000), seq(0,1,length.out=250), 
    rep(1,500), seq(-1,1,length.out=1000), rep(1,500))

z=rbind(x,y)

# Confirm the 'PT' is showing based on prompt code
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

# Create Identity Matrix
id_matrix <- diag(2)

# Create matrix for shear
shear_matrix <- matrix(c(1, 0, 1.2, 1), nrow=2, ncol=2) 

# Create matrix for scale
scale_matrix <- matrix(c(2, 0, 0, 2), nrow=2, ncol=2)

# Create matrix for rotation (90 degrees counterclockwise)
rot_matrix <- matrix(c(0, 1, -1, 0), nrow=2, ncol=2) 

# Create matrix for projection (projection on the y axis)
# Projection of 2D to 1D
proj_matrix <- matrix(c(0, 1, 0, 1), nrow=2, ncol=2)

# Make list of the transformation matrices to allow for looping
transforms <- list(id_matrix, shear_matrix, scale_matrix, rot_matrix, proj_matrix)

# Use x11 for Animation
x11(title="Animation")

# Loop the transformation matrices
# 5 displays total
for (idx in 1:5) {
  
  # Matrix multiple (apply transformation)
  z <- transforms[[idx]] %*% z
  
  # Display resulting plot
  plot(z[2,]~z[1,], xlim=c(-10,10), ylim=c(-10,10))
  
  # Add sleep so the animation will be easier to watch
  Sys.sleep(0.5)
}
```