---
title: "Animation by Matrix Multiplication"
subtitle: "DATA 605, Spring 2021: Assignment 1"
author: "Philip Tanofsky"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
---


## Prompt

For this assignment, build the first letters for both your first and last name using point plots in R.

Then, write R code that will left multiply (%>%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the identity matrix.  

Use a loop that changes the transformation matrix incrementally to demonstrate 1) shear, 2) scaling, 3)  rotation, and 4) projection in animated fashion.  

## Solution

Based on PDF output, code is located on page 1, page 2, page 22, page 42, page 62, page 82.

```{r}
library(animation)

# PT: Initials created by plot points
x=c(rep(-1,500), seq(-1,0,length.out=1000), seq(-1,0,length.out=1000),
    rep(0,250), seq(0.25,.75,length.out=500), rep(.75,1000), seq(.75,1.25,length.out=500))

y=c(seq(-1,1,length.out=500), rep(0,1000), rep(1,1000), seq(0,1,length.out=250), 
    rep(1,500), seq(-1,1,length.out=1000), rep(1,500))

# H (from prompt)
#x=c(rep(0,500), seq(0,1,length.out=1000), rep(1,500))
#y=c(seq(-1,1,length.out=500), rep(0,1000), seq(-1,1,length.out=500))
z=rbind(x,y)

# Confirm the 'PT' is showing based on prompt code
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

dev.control('enable')

anim = ani.record(reset = T, replay.cur = F)

# Create display window for animation
x11()

# Create 2x2 identity matrix
a=diag(2) 
#----------------------
# Scale animation
#----------------------
for (i in seq(3,-3, length.out=20)) {
  a[1,1] = i
  a[2,2] = i
  mod_mat = apply(z, 2, function(x) a%*%x)
  plot(mod_mat[2,]~mod_mat[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
}

# Reset 2x2 identity matrix
a=diag(2) 
#----------------------
# Shear
#----------------------
for (i in seq(3,-3, length.out=20)) {
  a[1,2] = i
  mod_mat = apply(z, 2, function(x) a%*%x)
  plot(mod_mat[2,]~mod_mat[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
}

# Reset 2x2 identity matrix
a=diag(2) 
#----------------------
# Projection on X axis (while X value scales)
#----------------------
for (i in seq(3,-3, length.out=20)) {
#  a[1,1] = i
  a[2,2] = i
  mod_mat = apply(z, 2, function(x) a%*%x)
  plot(mod_mat[2,]~mod_mat[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
}

# Define rotation function for matrix multiplication
rotate_func=function(x){matrix(c(cos(x), -sin(x), sin(x), cos(x)), byrow=T, nrow=2)}

# Reset 2x2 identity matrix
a=diag(2) 
#----------------------
# Rotation animation
#----------------------
for (i in seq(0,2, length.out=20)) {
  a=rotate_func(i)
  mod_mat = apply(z, 2, function(x) a%*%x)
  plot(mod_mat[2,]~mod_mat[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
}

saveGIF(ani.replay(), img.name = "initials_animation")

```

## Initial Solution Prior to Meetup

Including this solution I had which I believe technically met the criteria of the Assignment 1 prompt, but was inadequate after seeing the presentation during the first meet-up. Leaving here for posterity.

``` {r eval=F}
# PT
x=c(rep(-1,500), seq(-1,0,length.out=1000), seq(-1,0,length.out=1000),
    rep(0,250), seq(0.25,.75,length.out=500), rep(.75,1000), seq(.75,1.25,length.out=500))

y=c(seq(-1,1,length.out=500), rep(0,1000), rep(1,1000), seq(0,1,length.out=250), 
    rep(1,500), seq(-1,1,length.out=1000), rep(1,500))

z=rbind(x,y)

# Confirm the 'PT' is showing based on prompt code
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

# Create Identity Matrix
id_matrix <- diag(2)

# Create matrix for shear
shear_matrix <- matrix(c(1, 0, 1.2, 1), nrow=2, ncol=2) 

# Create matrix for scale
scale_matrix <- matrix(c(2, 0, 0, 2), nrow=2, ncol=2)

# Create matrix for rotation (90 degrees counterclockwise)
rot_matrix <- matrix(c(0, 1, -1, 0), nrow=2, ncol=2) 

# Create matrix for projection (projection on the y axis)
# Projection of 2D to 1D
proj_matrix <- matrix(c(0, 1, 0, 1), nrow=2, ncol=2)

# Make list of the transformation matrices to allow for looping
transforms <- list(id_matrix, shear_matrix, scale_matrix, rot_matrix, proj_matrix)

# Use x11 for Animation
x11(title="Animation")

# Loop the transformation matrices
# 5 displays total
for (idx in 1:5) {
  
  # Matrix multiple (apply transformation)
  z <- transforms[[idx]] %*% z
  
  # Display resulting plot
  plot(z[2,]~z[1,], xlim=c(-10,10), ylim=c(-10,10))
  
  # Add sleep so the animation will be easier to watch
  Sys.sleep(0.5)
}
```