---
title: "Problem Set 2"
subtitle: "DATA 605, Spring 2021: Assignment 2"
author: "Philip Tanofsky"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
---

# Prompt
Write an R function to factorize a square matrix $A$ into LU or LDU, whichever you prefer. Please submit your response in an R Markdown document.

You don’t have to worry about permuting rows of $A$ and you can assume that $A$ is less than $5 \times 5$, if you need to hard-code any variables in your code.

# Solution

Based on approach from "LU Decomposition Shortcut Method" video.

```{r}
# Using the algorithm from the LU Decomposition Shortcut Method video
# http://www.youtube.com/watch?v=UlWcofkUDDU

lu_decomposition <- function(matrix_in) {
  
  # Get row count of matrix
  n <- dim(matrix_in)[1]

  # Get column count of matrix  
  m <- dim(matrix_in)[2]

  # Return error message if matrix not a square
  if (n != m) {
    return("Error: Matrix not a square")
  }
  
  # Return error message if matrix too big
  if (n > 4) {
    return("Matrix greater than 4x4")
  }
  
  # Set upper matrix to input matrix
  upper <- matrix_in
  # Define lower matrix with diagonal (identity matrix)
  lower <- diag(n)
  
  # Outer loop to traverse the matrices top to bottom by row
  for (i in 2:n) {
    
    # Inner loop to traverse the matrices left to right by column
    for (j in 1:(i-1)) {
      
      # Calculate multiplier
      # Really, just divide the values and set lower matrix value per i,j
      lower[i,j] <- upper[i,j] / upper[j,j]
      
      # Calculate the row values for the upper matrix
      # Opposite of multiplier (lower value just set) mutiplied by above row in upper matrix
      # then added to row under consideration in upper matrix
      upper[i, ] <- -lower[i,j] * upper[j, ] + upper[i, ]
      }
  }
  
  # Outputs
  print("Input Matrix")
  print(matrix_in)
  print("Upper Matrix")
  print(upper)
  print("Lower Matrix")
  print(lower)
  
  # Return resulting upper and lower matrices
  return(list(upper,lower))
}
```

# Validations

```{r}
# Validations
#Not Square
#mat <- matrix(c(1, 2, 1, 2, 4, 3), nrow=2, ncol=3)
#Too big
#mat <- matrix(c(rep(2,36)), nrow=6, ncol=6)
#Invalid
#mat <- matrix(c(1, 2, 1, 2, 4, 3, 3, 5, 4), nrow=3, ncol=3)
#Valid
#mat <- matrix(c(2, -4, -4, -1, 6, -2, -2, 3, 8), nrow=3, ncol=3)
#Valid
mat <- matrix(c(-3, -12, 6, 0, -3, -15, 12, -15, 2, 6, 4, 6, 2, 12, -10, 29), nrow=4, ncol=4)

result <- lu_decomposition(mat)

# Output result
result

# If result was not an error, then compare results to original matrix
if (is.list(result)) {
  l_times_u <- result[[2]] %*% result[[1]]
  (mat == l_times_u)
}
```