---
title: "DATA 605: Assignment 2"
subtitle: "Semester: Spring 2021; Professor Doc Larry"
author: "Philip Tanofsky"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
---

# Problem Set 1

1. Show that $A^TA \neq AA^T$ in general. (Proof and demonstration.)

2. For a special type of square matrix $A$, we get $A^TA = AA^T$. Under what conditions
could this be true? (Hint: The Identity matrix I is an example of such a matrix).

## Part 1

Proof of $AA^T \neq A^TA$ in general.

In essence, prove matrix multiplication is not commutative. First, given a matrix $A$ with size $m \times n$, if $m \neq n$, then $AA^T$ would result in a $m \times m$ matrix while $A^TA$ would result in a $n \times n$ matrix. The resulting matrices are different sizes, and thus not equal.

### Proof

Now to prove $A^TA \neq AA^T$ in general for a square matrix.

Given a matrix

$$
A = 
\begin{bmatrix}
    a & b \\
    c & d \\
\end{bmatrix}
$$
With a transpose as
$$
A^T = 
\begin{bmatrix}
    a & c \\
    b & d \\
\end{bmatrix}
$$

Matrix multiply $AA^T$

$$
AA^T = 
\begin{bmatrix}
    a^2+b^2 & ac+bd \\
    ac+bd & c^2+d^2 \\
\end{bmatrix}
$$

Matrix multiply $A^TA$

$$
A^TA = 
\begin{bmatrix}
    a^2+c^2 & ab+cd \\
    ab+cd & b^2+d^2 \\
\end{bmatrix}
$$

Thus

$$
\begin{bmatrix}
    a^2+b^2 & ac+bd \\
    ac+bd & c^2+d^2 \\
\end{bmatrix}
\neq
\begin{bmatrix}
    a^2+c^2 & ab+cd \\
    ab+cd & b^2+d^2 \\
\end{bmatrix}
$$

### Demonstration

$$
A = 
\begin{bmatrix}
    1 & 3 \\
    2 & 4 \\
\end{bmatrix}
$$
With a transpose as
$$
A^T = 
\begin{bmatrix}
    1 & 2 \\
    3 & 4 \\
\end{bmatrix}
$$

Matrix multiply $AA^T$

$$
AA^T = 
\begin{bmatrix}
    10 & 14 \\
    14 & 20 \\
\end{bmatrix}
$$

Matrix multiply $A^TA$

$$
A^TA = 
\begin{bmatrix}
    5 & 11 \\
    11 & 25 \\
\end{bmatrix}
$$

Thus

$$
\begin{bmatrix}
    10 & 14 \\
    14 & 20 \\
\end{bmatrix}
\neq
\begin{bmatrix}
    5 & 11 \\
    11 & 25 \\
\end{bmatrix}
$$

#### Validation with R

```{r}
a = matrix(c(1,2,3,4), 2, 2)
at = matrix(c(1,3,2,4), 2, 2)

a

at

aat <- a %*% at

ata <- at %*% a

aat

ata

(aat == ata)
```

## Part 2

Under what conditions is $AA^T = A^TA$?

Answer: When matrix $A$ is **symmetric**. Thus $A = A^T$. And then, with substitution $AA = AA$.

$$
A = 
\begin{bmatrix}
    1 & 2 \\
    2 & 4 \\
\end{bmatrix}
$$
With a transpose as
$$
A^T = 
\begin{bmatrix}
    1 & 2 \\
    2 & 4 \\
\end{bmatrix}
$$

Matrix multiply $AA^T$

$$
AA^T = 
\begin{bmatrix}
    5 & 10 \\
    10 & 20 \\
\end{bmatrix}
$$

Matrix multiply $A^TA$

$$
A^TA = 
\begin{bmatrix}
    5 & 10 \\
    10 & 20 \\
\end{bmatrix}
$$

Thus

$$
\begin{bmatrix}
    5 & 10 \\
    10 & 20 \\
\end{bmatrix}
=
\begin{bmatrix}
    5 & 10 \\
    10 & 20 \\
\end{bmatrix}
$$

#### Validation with R

```{r}
a = matrix(c(1,2,2,4), 2, 2)
at = matrix(c(1,2,2,4), 2, 2)

a

at

aat <- a %*% at

ata <- at %*% a

aat

ata

(aat == ata)
```


# Problem Set 2

Write an R function to factorize a square matrix $A$ into LU or LDU, whichever you prefer. Please submit your response in an R Markdown document.

You don’t have to worry about permuting rows of $A$ and you can assume that $A$ is less than $5 \times 5$, if you need to hard-code any variables in your code.

## Solution

Based on approach from "LU Decomposition Shortcut Method" video.

```{r}
# Using the algorithm from the LU Decomposition Shortcut Method video
# http://www.youtube.com/watch?v=UlWcofkUDDU

lu_decomposition <- function(matrix_in) {
  
  # Get row count of matrix
  n <- dim(matrix_in)[1]

  # Get column count of matrix  
  m <- dim(matrix_in)[2]

  # Return error message if matrix not a square
  if (n != m) {
    return("Error: Matrix not a square")
  }
  
  # Return error message if matrix too big
  if (n > 4) {
    return("Matrix greater than 4x4")
  }
  
  # Set upper matrix to input matrix
  upper <- matrix_in
  # Define lower matrix with diagonal (identity matrix)
  lower <- diag(n)
  
  # Outer loop to traverse the matrices top to bottom by row
  for (i in 2:n) {
    
    # Inner loop to traverse the matrices left to right by column
    for (j in 1:(i-1)) {
      
      # Calculate multiplier
      # Really, just divide the values and set lower matrix value per i,j
      lower[i,j] <- upper[i,j] / upper[j,j]
      
      # Calculate the row values for the upper matrix
      # Opposite of multiplier (lower value just set) mutiplied by above row in upper matrix
      # then added to row under consideration in upper matrix
      upper[i, ] <- -lower[i,j] * upper[j, ] + upper[i, ]
      }
  }
  
  # Outputs
  print("Input Matrix")
  print(matrix_in)
  print("Upper Matrix")
  print(upper)
  print("Lower Matrix")
  print(lower)
  
  # Return resulting upper and lower matrices
  return(list(upper,lower))
}
```

## Validations

```{r}
# Validations
#Not Square
#mat <- matrix(c(1, 2, 1, 2, 4, 3), nrow=2, ncol=3)
#Too big
#mat <- matrix(c(rep(2,36)), nrow=6, ncol=6)
#Invalid
#mat <- matrix(c(1, 2, 1, 2, 4, 3, 3, 5, 4), nrow=3, ncol=3)
#Valid
#mat <- matrix(c(2, -4, -4, -1, 6, -2, -2, 3, 8), nrow=3, ncol=3)
#Valid
mat <- matrix(c(-3, -12, 6, 0, -3, -15, 12, -15, 2, 6, 4, 6, 2, 12, -10, 29), nrow=4, ncol=4)

result <- lu_decomposition(mat)

# Output result
result

# If result was not an error, then compare results to original matrix
if (is.list(result)) {
  l_times_u <- result[[2]] %*% result[[1]]
  (mat == l_times_u)
}
```
