---
title: "Problem Set 1"
subtitle: "DATA 605, Spring 2021: Assignment 2"
author: "Philip Tanofsky"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
---

# Prompt

1. Show that $A^TA \neq AA^T$ in general. (Proof and demonstration.)

2. For a special type of square matrix $A$, we get $A^TA = AA^T$. Under what conditions
could this be true? (Hint: The Identity matrix I is an example of such a matrix).

## Part 1

Proof of $AA^T \neq A^TA$ in general.

In essence, prove matrix multiplication is not commutative. First, given a matrix $A$ with size $m \times n$, if $m \neq n$, then $AA^T$ would result in a $m \times m$ matrix while $A^TA$ would result in a $n \times n$ matrix. The resulting matrices are different sizes, and thus not equal.

### Proof

Now to prove $A^TA \neq AA^T$ in general for a square matrix.

Given a matrix

$$
A = 
\begin{bmatrix}
    a & b \\
    c & d \\
\end{bmatrix}
$$
With a transpose as
$$
A^T = 
\begin{bmatrix}
    a & c \\
    b & d \\
\end{bmatrix}
$$

Matrix multiply $AA^T$

$$
AA^T = 
\begin{bmatrix}
    a^2+b^2 & ac+bd \\
    ac+bd & c^2+d^2 \\
\end{bmatrix}
$$

Matrix multiply $A^TA$

$$
A^TA = 
\begin{bmatrix}
    a^2+c^2 & ab+cd \\
    ab+cd & b^2+d^2 \\
\end{bmatrix}
$$

Thus

$$
\begin{bmatrix}
    a^2+b^2 & ac+bd \\
    ac+bd & c^2+d^2 \\
\end{bmatrix}
\neq
\begin{bmatrix}
    a^2+c^2 & ab+cd \\
    ab+cd & b^2+d^2 \\
\end{bmatrix}
$$

### Demonstration

$$
A = 
\begin{bmatrix}
    1 & 3 \\
    2 & 4 \\
\end{bmatrix}
$$
With a transpose as
$$
A^T = 
\begin{bmatrix}
    1 & 2 \\
    3 & 4 \\
\end{bmatrix}
$$

Matrix multiply $AA^T$

$$
AA^T = 
\begin{bmatrix}
    10 & 14 \\
    14 & 20 \\
\end{bmatrix}
$$

Matrix multiply $A^TA$

$$
A^TA = 
\begin{bmatrix}
    5 & 11 \\
    11 & 25 \\
\end{bmatrix}
$$

Thus

$$
\begin{bmatrix}
    10 & 14 \\
    14 & 20 \\
\end{bmatrix}
\neq
\begin{bmatrix}
    5 & 11 \\
    11 & 25 \\
\end{bmatrix}
$$

#### Validation with R

```{r}
a = matrix(c(1,2,3,4), 2, 2)
at = matrix(c(1,3,2,4), 2, 2)

a

at

aat <- a %*% at

ata <- at %*% a

aat

ata

(aat == ata)
```

## Part 2

Under what conditions is $AA^T = A^TA$?

Answer: When matrix $A$ is **symmetric**. Thus $A = A^T$. And then, with substitution $AA = AA$.

$$
A = 
\begin{bmatrix}
    1 & 2 \\
    2 & 4 \\
\end{bmatrix}
$$
With a transpose as
$$
A^T = 
\begin{bmatrix}
    1 & 2 \\
    2 & 4 \\
\end{bmatrix}
$$

Matrix multiply $AA^T$

$$
AA^T = 
\begin{bmatrix}
    5 & 10 \\
    10 & 20 \\
\end{bmatrix}
$$

Matrix multiply $A^TA$

$$
A^TA = 
\begin{bmatrix}
    5 & 10 \\
    10 & 20 \\
\end{bmatrix}
$$

Thus

$$
\begin{bmatrix}
    5 & 10 \\
    10 & 20 \\
\end{bmatrix}
=
\begin{bmatrix}
    5 & 10 \\
    10 & 20 \\
\end{bmatrix}
$$

#### Validation with R

```{r}
a = matrix(c(1,2,2,4), 2, 2)
at = matrix(c(1,2,2,4), 2, 2)

a

at

aat <- a %*% at

ata <- at %*% a

aat

ata

(aat == ata)
```
