---
title: "DATA 605 Assignment Week 15"
subtitle: 'CUNY Spring 2021'
author: "Philip Tanofsky" 
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
   - \usepackage{amsmath}
output: pdf_document
---

# Exercise 1
Find the equation of the regression line for the given points. Round any final values to the nearest hundredth, if necessary.

(5.6,8.8), (6.3,12.4), (7,14.8), (7.7,18.2), (8.4,20.8)

### Answer

```{r warning=F, message=F}
x <- c(5.6, 6.3, 7, 7.7, 8.4)
y <- c(8.8, 12.4, 14.8, 18.2, 20.8)

model <- lm(y~x)

model
```

$$y = -14.80 + 4.28x$$

# Exercise 2
Find all local maxima, local minima, and saddle points for the function given below. Write your answer(s) in the form $(x, y, z)$. Separate multiple points with a comma.

$$f(x,y)=24x-6xy^2-8y^3$$

### Answer

First partial derivatives

$$f_x(x,y) = 24 - 6y^2$$
$$f_y(x,y) = -12xy - 24y^2$$

If $24 - 6y^2 = 0$, then $y^2 = 4$ and thus $y \pm 2$.

If $y = 2$ and $-12xy - 24y^2 = 0$, then $-24x = 24(2^2)$ and thus $x = -4$.

If $y = -2$ and $-12xy - 24y^2 = 0$, then $24x = 24(2^2)$ and thus $x = 4$.

Now, calculate $f(x,y)$.

$$f(4,-2) = 24(4) - 6(4)(-2^2) - 8(-2^3)$$
$$= 96 - 96 + 64$$
$$f(4,-2) = 64$$
$$f(-4,2) = 24(-4) - 6(-4)(2^2) - 8(2^3)$$
$$= -96 + 96 - 64$$
$$f(-4,2) = -64$$

Two Critical Points
$(4, -2, 64)$ and $(-4,2,-64)$

Now, use the Second Derivative Test to determine if the points are local maxima, local minima, or saddle points.

Second Derivatives

$f_{xx} = 0$ and $f_{yy} = -12x - 48y$ and $f_{xy} = -12y$

Consider

$$D(x,y) = f_{xx}f_{yy} - f_{xy}^2$$
$$= (0)(-12x - 48y) - (-12y)^2$$
$$= -144y^2$$
$D(x,y) < 0$ for all $(x, y)$, thus any critical point is a saddle points.

Therefore both critical points $(4, -2)$ and $(-4, 2)$ are saddle points.

# Exercise 3
A grocery store sells two brands of a product, the "house" brand and a "name" brand. The manager estimates that if she sells the "house" brand for $x$ dollars and the "name" brand for $y$ dollars, she will be able to sell $81-21x+17y$ units of the "house" brand and $40+11x-23y$ units of the "name" brand.

## Step 1

Find the revenue function $R (x, y)$.

### Answer

House Brand
$$R(x) = (81-21x+17y) \times x$$

Name Brand
$$R(y) = (40+11x-23y) \times y$$
Combine $R(x)$ and $R(y)$ to create revenue function $R(x,y)$

$$R(x,y) = R(x) + R(y)$$
$$= (81-21x+17y)x + (40+11x-23y)y$$
$$= 81x-21x^2+17yx + 40y+11xy-23y^2$$
$$R(x,y) = 28xy - 21x^2 - 23y^2 + 81x + 40y$$

## Step 2
What is the revenue if she sells the "house" brand for \$2.30 and the "name" brand for \$4.10?

### Answer
```{r warning=F, message=F}
#house price
house <- 2.3
#name price
name <- 4.1

revenue <- function(x, y) {
  return ((28 * x * y) - (21 * x**2) - (23 * y**2) + (81 * x) + (40 * y))
}

revenue(house, name)
```

Total revenue: $`r revenue(house, name)`.

# Exercise 4
A company has a plant in Los Angeles and a plant in Denver. The firm is committed to produce a total of 96 units of a product each week. The total weekly cost is given by $C(x,y)=\frac{1}{6}x^2 + \frac{1}{6}y^2 + 7x + 25y + 700$, where $x$ is the number of units produced in Los Angeles and $y$ is the number of units produced in Denver. How many units should be produced in each plant to minimize the total weekly cost?

$$C(x,y)=\frac{1}{6}x^2 + \frac{1}{6}y^2 + 7x + 25y + 700$$

### Answer

From the prompt, $x + y = 96$, thus $x = 96 - y$.

$$C(x,y) = C(96-y,y)$$
$$=\frac{1}{6}x^2 + \frac{1}{6}y^2 + 7x + 25y + 700$$
$$=\frac{1}{6}(96-y)^2 + \frac{1}{6}y^2 + 7(96-y) + 25y + 700$$
$$=\frac{1}{6}(y^2-192y + 9216) + \frac{1}{6}y^2 + 672 - 7y + 25y + 700$$
$$=\frac{1}{6}y^2 - 32y + 1536 + \frac{1}{6}y^2 + 18y + 1372$$
$$C(y)=\frac{1}{3}y^2 - 14y + 2908$$

Now, to find the minimal value, let's take the derivative at set that to zero:

$$C'(y) = \frac{2}{3}y - 14$$
$$0 = \frac{2}{3}y - 14$$
$$0 = \frac{2}{3}y - 14$$
$$21 = y$$

Denver should produce 21 units. Thus LA should produce (x = 96 - y ... x = 96 - 21) 75 units.


# Exercise 5
Evaluate the double integral on the given region.

$$\iint (e^{8x+3y})\ dA;R:2 \leq x \leq 4\ and\ 2 \leq y \leq 4$$

Write your answer in exact form without decimals.

### Answer

$$\int_2^4 \int_2^4 (e^{8x+3y})\ dy\ dx$$
$$= \int_2^4 \bigg(\bigg[\frac{1}{3}e^{8x+3y}\bigg]\bigg|_2^4\bigg)\ dx$$
$$= \int_2^4 \bigg(\bigg[\frac{1}{3}e^{8x+12}\bigg]-\bigg[\frac{1}{3}e^{8x+6}\bigg]\bigg)\ dx$$
$$= \int_2^4 \bigg(\frac{1}{3}e^{8x+6}\bigg[e^{6}-1\bigg]\bigg)\ dx$$
$$= \bigg(\frac{1}{24}e^{8x+6}\bigg[e^{6}-1\bigg]\bigg)\bigg|_2^4$$

$$= \frac{1}{24}e^{38}(e^{6}-1)-\frac{1}{24}e^{22}(e^{6}-1)$$
$$= \frac{1}{24}(e^{38}-e^{22)}(e^{6}-1)$$
$$= \frac{1}{24}(e^{44}-e^{38}-e^{28}+e^{22})$$

