---
title: 'DATA 605: Assignment 8'
subtitle: 'CUNY Spring 2021'
author: "Philip Tanofsky" 
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
   - \usepackage{amsmath}
output: pdf_document
---

# Problem 1

The price of one share of stock in the Pilsdorff Beer Company (see Exercise 8.2.12) is given by $Y_n$ on the $n$th day of the year. Finn observes that the differences $X_n = Y_{n+1} - Y_n$ appear to be independent random variables with a common distribution having mean $\mu = 0$ and variance $\sigma^2 = 1/4$. If $Y_1 = 100$, estimate the probability that $Y_{365}$ is

## A: $\geq$ 100
$$
P(Y_{365}-Y_1 \geq 0)
$$


```{r warning=F,message=F}
y.1 <- 100
mu <- 0
var <- 1/4
sd <- sqrt(var)

y.365 <- 100
x.a <- (y.365 - y.1) / sqrt(365-1)
a.result <- pnorm(x.a, mean = mu, sd = sd, lower.tail=F)
a.result
```

## B: $\geq$ 110
$$
P(Y_{365}-Y_1 \geq 10)
$$

```{r warning=F,message=F}
y.365 <- 110
x.b <- (y.365 - y.1) / sqrt(365-1)
b.result <- pnorm(x.b, mean = mu, sd = sd, lower.tail=F)
b.result
```

## C: $\geq$ 120

$$
P(Y_{365}-Y_1 \geq 20)
$$

```{r warning=F,message=F}
y.365 <- 120
x.c <- (y.365 - y.1) / sqrt(365-1)
c.result <- pnorm(x.c, mean = mu, sd = sd, lower.tail=F)
c.result
```

# Problem 2

Calculate the expected value and variance of the binomial distribution using the moment generating function.

## Answer

### Expected Value

Binomial distribution: probability mass function

$$
P_X(j) = {n \choose x}p^xq^{n-x}\ with\ q=1-p
$$

Moment generating function definition

$$
M(t) = E(e^{tX}) = \sum_{x \epsilon S}^{} e^{tx}f(x)
$$

Substitute the binomial distribution function into mgf

$$
\begin{split}
= \sum_{x=0}^{n} e^{tx}{n \choose x}p^xq^{n-x} \\
= \sum_{x=0}^{n} (pe^t)^x{n \choose x}q^{n-x} \\
= (q+pe^t)^n
\end{split}
$$

The final equality represents the expansion of the binomial. Now, differentiate the moment generating function with respect to $t$ using the function-of-a-function rule, results in

$$
\begin{split}
\frac{dM_x(t)}{dt}=n(q+pe^t)^{n-1}pe^t \\ = npe^t(q+pe^t)^{n-1}
\end{split}
$$

Evaluate with $t=0$ results in expected value ...

$$
E(x)=np(q+p)^{n-1}=np
$$

### Variance

To find the second moment, use the product rule

$$
\frac{duv}{dx} = u\frac{dv}{dx}+v\frac{du}{dx}
$$

expanding and substituting

$$
\begin{split}
\frac{d^2M_x(t)}{dt^2}=npe^t \{(n-1)(q+pe^t)^{n-2}pe^t\} + (q+pe^t)^{n-1}\{npe^t\} \\ =npe^t(q+pe^t)^{n-2}\{(n-1)pe^t + (q+pe^t)\} \\ 
= npe^t(q+pe^t)^{n-2}\{q+npe^t\}
\end{split}
$$

Evaluate with $t=0$, results in

$$
E(x^2)=np(q+p)^{n-2}(q+np) \\ =np(q + np)
$$

Now, we can calculate the Variance

$$
V(x) = E(x2) - \{E(x)\}^2 \\ =np(q+np) -n^2p^2 \\ =npq
$$

Or, substituting for $q = 1-p$, variance is ...

$$
V(x) = np(1-p)
$$

Definitely took help from: https://www.le.ac.uk/users/dsgp1/COURSES/MATHSTAT/5binomgf.pdf

# Problem 3

Calculate the expected value and variance of the exponential distribution using the moment generating function.

## Answer
Exponential distribution function is

$$
f(x)=\lambda e^{-\lambda x}
$$

with 

$$
f_{X}(x) = \begin{cases}
  \lambda e^{-\lambda x}, & \text{if } x \geq 0, \\
  0, & \text{otherwise}.
\end{cases} 
$$

Moment generating function is

$$
M_x(t)=E(e^tX)= \int_{-\infty}^{\infty}e^{tx}f_X(x)dx
$$

Now, integrating by method of substitution

$$
\begin{split}
M_X(t) = \int_{-\infty}^{\infty}e^{tx}\lambda e^{-\lambda x}dx \\ 
=\lambda \int_{0}^{\infty}e^{(t-\lambda)x}dx \\ 
= \frac{\lambda}{t-\lambda}\ provided\ that\ |t| < \lambda
\end{split}
$$

Define theorem, if $X$ has mgf $M_X(t)$, then

$$
E(X^n)=M_X^{(n)}(0)
\\
where
\\
M_X^{(n)}(0) = \frac{d^n}{dt^n}M_X(t)|_0
$$

That means, the n-th moment is equal to the n-th derivative of the mgf evaluated at $t=0$.

Now using above theorem, evaluate the first and second moments

First Moment

$$
E(X) = M_X^{(1)}(0) = \frac{\lambda}{(\lambda-t)^2}|_{t=0} = \frac{1}{\lambda}
$$

Second Moment

$$
E(X^2) = M_X^{(2)}(0) = \frac{2\lambda}{(\lambda-t)^3}|_{t=0} = \frac{2}{\lambda^2}
$$

### Expected Value

From first moment, expected value is
$$
E(X) = \frac{1}{\lambda}
$$

### Variance

Based on first and second moment, variance is
$$
var(X) = E(X^2) - [E(X)]^2 = \frac{2}{\lambda^2} - \frac{1}{\lambda^2} = \frac{1}{\lambda^2}
$$


Definitely took help from: http://www.maths.qmul.ac.uk/~bb/MS_Lectures_5and6.pdf